A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-10-07 latex/main.tex
Add draft figures and document table

\begin{table}
\caption{RIPPLES pango X lineage events.} 
\label{tab:ripples_x_lineages}
\centering
\begin{scriptsize}

\begin{tabular}{lrrlrl}
\toprule
pango & in p4 & UShER desc & sc2ts class & clade diff & descendants \\
\midrule
XBR & $\checkmark$ & 1 & I & 0 & {XBR:1} \\
XM3 & $\checkmark$ & 1 & I & 0 & {XM:1} \\
XC & $\checkmark$ & 5 & I & 0 & {XC:5} \\
XBM & $\checkmark$ & 12 & I & 0 & {XBM:10, BF.3:2} \\
XS & $\checkmark$ & 17 & I & 0 & {XS:17} \\
XY &  & 23 & I & 0 & {XY:23} \\
XW &  & 32 & I & 0 & {XW:32} \\
XA & $\checkmark$ & 39 & I & 0 & {XA:39} \\
XL &  & 64 & I & 0 & {XL:64} \\
XBB &  & 6452 & I & 1 & {XBB:2361} \\
\midrule
XQ &  & 1 & II & 0 & {XAM:1} \\
XM & $\checkmark$ & 8 & II & 0 & {BA.2:4, XM:4} \\
Xx &  & 9 & II & 0 & {XAE:9} \\
Xx & $\checkmark$ & 18 & II & 0 & {XAC:18} \\
XQ &  & 21 & II & 0 & {XAM:21} \\
XE/XH &  & 1113 & II & 3 & {XE:1113} \\
\midrule
XB & $\checkmark$ & 411 & IV & 0 & {B.1:219, XB:192} \\
\midrule
NA & $\checkmark$ & 19 & NA & 45190 & {XAJ:18, BA.4:1} \\
NA &  & 20 & NA & 1061775 & {BA.1.15:1, XS:17, BA.1:1, BA.1.1:1} \\
NA & $\checkmark$ & 35 & NA & 7147 & {XBD:30, BA.2.75:5} \\
NA & $\checkmark$ & 36 & NA & 7146 & {XBD:30, XBR:1, BA.2.75:5} \\
NA &  & 1321 & NA & 340501 & {XE:1113, XH:2, XJ:68, XY:23, BA.2:82, XM:29,
XAL:3, XAF:1} \\
\bottomrule
\end{tabular}

@@

>>>>

Table~\ref{tab:ripples_x_lineages}
Figure \ref{fig:ripples_sc2ts_events}

\begin{table}
\caption{RIPPLES Pango X lineage events. Each row is a recombination event
identified by RIPPLEs (at p=3) in which X lineages appear, along with the 
corresponding sc2ts event from Table~\ref{tab:pango_x_lineages}, where
applicable, grouped by class. 
Events also present at p=4 are indicated. Clades are matched 
by finding the most recent common ancestor
of the samples associated with each UShER/RIPPLES event in 
the sc2ts ARG. The clade differences indicates how close this match
is. The final group of rows shows events that cannot be reasonably
mapped between UShER and sc2ts, where placement of one or more samples
differed significantly.}
\label{tab:ripples_x_lineages}
\centering
\begin{scriptsize}

\begin{tabular}{lrrlrl}
\toprule
pango & in p4 & UShER desc & sc2ts class & clade diff & descendants \\
\midrule
XBR & $\checkmark$ & 1 & I & 0 & {XBR:1} \\
XM3 & $\checkmark$ & 1 & I & 0 & {XM:1} \\
XC & $\checkmark$ & 5 & I & 0 & {XC:5} \\
XBM & $\checkmark$ & 12 & I & 0 & {XBM:10, BF.3:2} \\
XS & $\checkmark$ & 17 & I & 0 & {XS:17} \\
XY &  & 23 & I & 0 & {XY:23} \\
XW &  & 32 & I & 0 & {XW:32} \\
XA & $\checkmark$ & 39 & I & 0 & {XA:39} \\
XL &  & 64 & I & 0 & {XL:64} \\
XBB &  & 6452 & I & 1 & {XBB:2361} \\
\midrule
XQ &  & 1 & II & 0 & {XAM:1} \\
XQ &  & 21 & II & 0 & {XAM:21} \\
XM & $\checkmark$ & 8 & II & 0 & {BA.2:4, XM:4} \\
Xx &  & 9 & II & 0 & {XAE:9} \\
Xx & $\checkmark$ & 18 & II & 0 & {XAC:18} \\
XE/XH &  & 1113 & II & 3 & {XE:1113} \\
\midrule
XB & $\checkmark$ & 411 & IV & 0 & {B.1:219, XB:192} \\
\midrule
NA & $\checkmark$ & 19 & NA & 45190 & {XAJ:18, BA.4:1} \\
NA &  & 20 & NA & 1061775 & {BA.1.15:1, XS:17, BA.1:1, BA.1.1:1} \\
NA & $\checkmark$ & 35 & NA & 7147 & {XBD:30, BA.2.75:5} \\
NA & $\checkmark$ & 36 & NA & 7146 & {XBD:30, XBR:1, BA.2.75:5} \\
NA &  & 1321 & NA & 340501 & {XE:1113, XH:2, XJ:68, XY:23, BA.2:82, XM:29,
XAL:3, XAF:1} \\
\bottomrule
\end{tabular}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[]{ripples_p4_sc2ts_events.pdf}&
\includegraphics[]{ripples_p3_sc2ts_events.pdf}\\
\end{tabular}
\caption{TODO caption}
\label{fig:ripples_sc2ts_events}
\end{figure}
